---
title: "Training resources"
description: "Curated courses and learning materials for infectious disease modelling, epidemiological statistics, mathematical epidemiology, stochastic processes, and network science."
execute:
  echo: false
  warning: false
  message: false
---

This page collects selected courses, summer schools, online materials, textbooks, and tutorials for infectious disease modelling and adjacent methods.

The list is manually curated. Course dates, fees, eligibility, and application deadlines may change; always check the official page. The `last_checked` field in the CSV records when each entry was last reviewed.

## Suggested routes

| Goal | Suggested resources |
|---|---|
| Regression and epidemiological statistics | Imperial/Coursera public-health R specialization; Nahhas book; Wageningen Advanced Analytical Epidemiology |
| Basic infectious disease modelling | FUN-MOOC or Imperial/Coursera Infectious Disease Modelling; LSHTM introduction course |
| Implementing transmission models | LSHTM Modern Techniques in Infectious Disease Modelling |
| Fitting infectious disease dynamic models | Statistical Rethinking; LSHTM Model Fitting and Inference |
| Mathematical epidemiology | Diekmann, Heesterbeek & Britton; Keeling & Rohani |
| Stochastic epidemic models | ESPIDAM stochastic epidemic models course; Allen primer; Britton notes |
| Network and contact-pattern modelling | Utrecht Network Science; ESPIDAM Networks and contact patterns; SISMID Network Modeling for Epidemics |
| Stochastic-process foundations | MIT OCW Introduction to Stochastic Processes; MITx Probability |

```{r}
# Helpers -----------------------------------------------------------------

csv_candidates <- c(
  "data/training_resources.csv",
  "resources/data/training_resources.csv"
)

csv_path <- csv_candidates[file.exists(csv_candidates)][1]

if (is.na(csv_path)) {
  stop("Could not find data/training_resources.csv. Place it in resources/data/training_resources.csv.")
}

resources <- read.csv(
  csv_path,
  stringsAsFactors = FALSE,
  check.names = FALSE,
  encoding = "UTF-8"
)

category_order <- c(
  "Epidemiological statistics and regression",
  "Infectious disease modelling and outbreak analytics",
  "Mathematical epidemiology and stochastic epidemic models",
  "Probability and stochastic processes",
  "Network science, complex systems, and ABM",
  "Books, papers, and reference materials"
)

relevance_order <- c("core", "recommended", "specialized", "reference", "archived")

resources$category <- factor(resources$category, levels = category_order)
resources$relevance_rank <- match(resources$relevance, relevance_order)
resources <- resources[order(resources$category, resources$relevance_rank, resources$title), ]

md_escape <- function(x) {
  x <- ifelse(is.na(x), "", x)
  x <- gsub("\\|", "\\\\|", x)
  x <- gsub("\n", " ", x)
  x
}

short_topics <- function(x, n = 4) {
  x <- ifelse(is.na(x), "", x)
  parts <- trimws(strsplit(x, ";", fixed = TRUE)[[1]])
  parts <- parts[nzchar(parts)]
  if (length(parts) <= n) {
    paste(parts, collapse = "; ")
  } else {
    paste0(paste(parts[seq_len(n)], collapse = "; "), "; …")
  }
}

render_category <- function(category_name) {
  d <- resources[as.character(resources$category) == category_name, ]

  cat("\n## ", category_name, "\n\n", sep = "")

  if (nrow(d) == 0) {
    cat("_No entries._\n\n")
    return(invisible(NULL))
  }

  cat("| Resource | Provider | Level | Status | Focus |\n")
  cat("|---|---|---|---|---|\n")

  for (i in seq_len(nrow(d))) {
    title <- md_escape(d$title[i])
    url <- d$url[i]
    provider <- md_escape(d$provider[i])
    level <- md_escape(d$level[i])
    status <- md_escape(d$status[i])
    focus <- md_escape(short_topics(d$topics[i]))

    cat(
      "| [", title, "](", url, ") ",
      "| ", provider,
      " | ", level,
      " | ", status,
      " | ", focus,
      " |\n",
      sep = ""
    )
  }

  cat("\n")
}
```

```{r, results='asis'}
for (cat_name in category_order) {
  render_category(cat_name)
}
```

## Notes on status and relevance

| Field | Meaning |
|---|---|
| `core` | Strongly useful for training in infectious disease modelling or epidemiological methods |
| `recommended` | Broadly useful, but not necessarily essential |
| `specialized` | Highly useful for a specific topic or method |
| `reference` | Useful as supporting material or self-study |
| `self-paced` | Stable online material, book, or tutorial |
| `recurring` | Course or event appears to run repeatedly, although details may change |
| `unknown` | Status should be checked again |

## Maintenance

The source of truth is [`data/training_resources.csv`](data/training_resources.csv). To update the page, edit the CSV and render the site again.

Suggested maintenance rules:

- keep one resource per row;
- update `last_checked` whenever an entry is reviewed;
- use official course pages as URLs whenever possible;
- keep `notes` short;
- do not delete past courses immediately if they are likely to recur;
- use `status = unknown` when the current status is unclear.

Inclusion in this list does not imply endorsement by any affiliated institution.
