---
title: "Training resources"
description: "Curated courses and learning materials for infectious disease modelling, epidemiological statistics, mathematical epidemiology, stochastic processes, and network science."
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

This page lists selected courses, summer schools, online materials, textbooks, and tutorials for infectious disease modelling, epidemiological statistics, mathematical epidemiology, stochastic processes, and network science.

The list is manually curated. Course dates, fees, eligibility, and application deadlines may change; always check the official page. The `last_checked` field records when I last reviewed each entry.

```{r}
library(readr)
library(dplyr)
library(gt)
library(stringr)

resources <- read_csv("data/training_resources.csv", show_col_types = FALSE)

make_resource_table <- function(data) {
  data |>
    transmute(
      Resource = md(str_glue("[{title}]({url})")),
      Provider = provider,
      Mode = mode,
      Level = level,
      Status = status,
      Relevance = relevance,
      Topics = topics,
      Notes = notes,
      `Last checked` = last_checked
    ) |>
    gt() |>
    tab_options(
      table.font.size = px(13),
      data_row.padding = px(6)
    ) |>
    cols_width(
      Resource ~ px(250),
      Provider ~ px(180),
      Mode ~ px(90),
      Level ~ px(100),
      Status ~ px(100),
      Relevance ~ px(110),
      Topics ~ px(280),
      Notes ~ px(320),
      `Last checked` ~ px(110)
    )
}

category_order <- c(
  "Epidemiological statistics and regression",
  "Infectious disease modelling and outbreak analytics",
  "Mathematical epidemiology and stochastic epidemic models",
  "Probability and stochastic processes",
  "Network science, complex systems, and ABM",
  "Books, papers, and reference materials"
)

resources <- resources |>
  mutate(category = factor(category, levels = category_order)) |>
  arrange(category, relevance, title)
```

## Suggested routes

These routes are subjective and intended as quick orientation rather than a formal curriculum.

| Goal | Suggested resources |
|---|---|
| Regression and epidemiological statistics | Imperial/Coursera public-health R specialization; Nahhas book; Wageningen Advanced Analytical Epidemiology |
| Basic infectious disease modelling | FUN-MOOC or Imperial/Coursera Infectious Disease Modelling; LSHTM introduction course |
| Implementing transmission models | LSHTM Modern Techniques in Infectious Disease Modelling |
| Fitting infectious disease dynamic models | Statistical Rethinking; LSHTM Model Fitting and Inference |
| Mathematical epidemiology | Diekmann, Heesterbeek & Britton; Keeling & Rohani |
| Stochastic epidemic models | ESPIDAM stochastic epidemic models course; Allen primer; Britton notes |
| Network and contact-pattern modelling | Utrecht Network Science; ESPIDAM Networks and contact patterns; SISMID Network Modeling for Epidemics |
| Stochastic-process foundations | MIT OCW Introduction to Stochastic Processes; MITx Probability |

## Epidemiological statistics and regression

```{r}
resources |>
  filter(category == "Epidemiological statistics and regression") |>
  make_resource_table()
```

## Infectious disease modelling and outbreak analytics

```{r}
resources |>
  filter(category == "Infectious disease modelling and outbreak analytics") |>
  make_resource_table()
```

## Mathematical epidemiology and stochastic epidemic models

```{r}
resources |>
  filter(category == "Mathematical epidemiology and stochastic epidemic models") |>
  make_resource_table()
```

## Probability and stochastic processes

```{r}
resources |>
  filter(category == "Probability and stochastic processes") |>
  make_resource_table()
```

## Network science, complex systems, and ABM

```{r}
resources |>
  filter(category == "Network science, complex systems, and ABM") |>
  make_resource_table()
```

## Books, papers, and reference materials

```{r}
resources |>
  filter(category == "Books, papers, and reference materials") |>
  make_resource_table()
```

## Maintenance notes

- `data/training_resources.csv` is the source of truth.
- Keep this `.qmd` page short; update entries in the CSV rather than editing tables by hand.
- Use `status = self-paced` for stable online materials and books.
- Use `status = recurring` for courses that appear to run repeatedly, even when the current year's edition has passed.
- Move uncertain or outdated entries to `status = unknown` rather than deleting them immediately.
- Update `last_checked` whenever an entry is reviewed.
- Inclusion in this list does not imply endorsement by any affiliated institution.
